PODD Ontology Driven Database

### 2012-03-12 epncanberra2012/Podd-20120313.tex
more minor edits
grammar check

%\usepackage{beamerthemeBerkeley}
\usetheme{Berkeley}

@@

@@

\begin{itemize}
 \item PODD implemented between 2009 and 2011
 \item Design by Yuan Fang Li and Gavin Kennedy for High Resolution Plant Phenomics Centre
\end{itemize}

@@

Good:

\begin{enumerate}
 \item Flexible : Simultaneously support different experiments
 \item Adaptable : Additions and changes to schema ontologies
\end{enumerate}

Bad:

@@

\begin{itemize}
 \item Use upcoming SPARQL 1.1 Query and Update standards
 \item Use OWL-2 and pure SPARQL access to databases
 \item Support links from experiments to other RDF documents
\end{itemize}

>>>>

@@

\usetheme{Berkeley}

@@

\begin{itemize}
 \item PODD implemented between 2009 and 2011
 \item Design by Yuan Fang Li and Gavin Kennedy for the High Resolution Plant Phenomics Centre
\end{itemize}

@@

Pros:

\begin{enumerate}
 \item Flexible : Simultaneously supports different experiments
 \item Adaptable : Supports additions and changes to schema ontologies
\end{enumerate}

Cons:

@@

\begin{itemize}
 \item Use upcoming SPARQL 1.1 Query and Update standards
 \item Support OWL-2
 \item Pure SPARQL access using a single database
 \item Support links from experiments to other RDF documents
\end{itemize}
